---
title: "NYTimes_API"
author: "ODONNELL"
date: "March 31, 2019"
output: html_document
---

Assignment: Construct an interface in R to read in JSON data
from a NY Times API and turn it into a dataframe.

storing my API Key
```{r}
NYTIMES_KEY="LCb20T9B6ElAt06GRGVlGzyl3PNF7Kzq"
```

load jsonlite package
```{r}
library(jsonlite)
```

search National Parks articles from the NY Times API
```{r}
library(tidyr)
library(dplyr)

NYTimes_df <- fromJSON("http://api.nytimes.com/svc/search/v2/articlesearch.json?q=national+park&api-key=LCb20T9B6ElAt06GRGVlGzyl3PNF7Kzq", flatten = TRUE) %>% data.frame()
```

Cool! Now the information about National Park articles on NY Times
is stored as a DataFrame.

Now, to clean up the dataframe

removing some unneeded columns
```{r}
NYTimes_df <- NYTimes_df %>%
  select(response.docs.headline.main, response.docs.byline.original,
         response.docs.type_of_material, response.docs.news_desk,
         response.docs.source, response.docs.abstract,
         response.docs.word_count, response.docs.snippet,
         response.docs.lead_paragraph, response.docs.keywords)
```

For fun, some high level frequency counts
```{r}
NYTimes_df %>%
  group_by(response.docs.type_of_material, response.docs.news_desk) %>%
  summarise(freq = n()) %>%
  arrange(desc(freq))
```

```{r}
NYTimes_df %>%
  group_by(response.docs.byline.original) %>%
  summarise(freq = n()) %>%
  arrange(desc(freq))
```


